\documentclass[12pt, a4paper]{article}

\input{internal/packages}
\input{internal/formatting}
\input{internal/macros}

\phone{+44 (0)7834 xxx xxx}
\locationurl{https://goo.gl/maps/bEk6nHTSkGxsFm4y6}
\location{Newcastle upon Tyne, UK}
\email{jwalton3141@gmail.com}
\linkedin{jwalton93}
\website{jwalton.info}
\stackoverflow{11021886}
\github{jwalton3141}

\begin{document}



\name{Dr. Jack Walton}

\makecard

\statement{Self-driven, adaptable and passionate technologist, with expertise
in data engineering and data science, seeks challenging and intellectually
stimulating work in a fast-paced environment.}



\cvsection{Education}

\eduitem{University of Newcastle upon Tyne, UK}%
        {PhD, Applied Mathematics\\
         \href{https://jwalton.info/assets/thesis.pdf}%
              {{\footnotesize\faIcon{paperclip}}``Bayesian Inference for Models of Collective Behaviour''}}%
        {2016--2020}

\eduitem{University of Newcastle upon Tyne, UK}%
        {Master of Mathematics, 1st Class}%
        {2012--2016}



\cvsection{Experience}

\jobitem{Data Engineer \& Trainer}%
        {\href{https://www.jumpingrivers.com/}{Jumping Rivers Ltd.}}%
        {2020--Present}

\vspace{-1em}

\cvsubsection{Notable Client Projects}

\faitem{\faIcon{aws}}{3.25em}%
       {\emph{Serverless \& massively scalable web app with AWS\hfill{}Lead Developer}

       \begin{adjustwidth}{0em}{3em}

       \sloppy{}Used Docker to productionise a Bayesian network model,
       and parameterised PDF report and data visualisation generation,
       via AWS Lambda and API Gateway
       (\href{https://github.com/nationalarchives/diagram/tree/live/api}%
             {\texttt{github.com/nationalarchives/DiAGRAM/tree/live/api}}).

       Developed Terraform for IaC, provisioning development, staging and production environments
       (\href{https://github.com/nationalarchives/DiAGRAM-terraform/}%
             {\texttt{github.com/nationalarchives/DiAGRAM-terraform}}).

       Automated front and backend deployment, controlling application life
       cycle with GitHub and GitHub Actions.

       \end{adjustwidth}}%

\faitem{\faIcon{microsoft}}{3.25em}%
       {\emph{Azure Databricks \& App Service for emergency response
           coordination\hfill{}Lead Developer}

       \begin{adjustwidth}{0em}{3em}

       Created Databricks init scripts to install custom ETL R package from Azure
       Repos.

       Adapted existing ETL R scripts to write results to blob storage via
       \href{https://cran.r-project.org/web/packages/AzureStor/vignettes/intro.html}%
            {\{AzureStor\}}.

       Improved typical application deploy time from $\sim$20mins to $\sim$2--3mins.

       \end{adjustwidth}}%

\vspace{-.4em}

\cvsubsection{Responsibilities \& Achievements}

\begin{itemize}[
    itemsep=.2em,
    labelwidth=2em,
    leftmargin=3.25em,
    topsep=0em]

     \item[\faIcon{python}]%
       {Taught over 250 hours of Python programming courses, with course difficulty
        ranging from ``what is a variable?'' to machine learning with \texttt{sklearn}.}%

     \item[\faIcon{layer-group}]%
       {Training tech stack product owner; prioritised, performed and delegated development and
       maintenance work to support delivery of $\sim$150 JR training courses per
       annum.}

    \item[\faIcon{cloud}]%
       {Employed Ansible and Terraform to manage, provision and configure client and
        internal infrastructure, working with a number of different cloud
        providers (Azure, AWS, and DigitalOcean).}%

     \item[\faIcon{chalkboard-teacher}]%
       {Developed and delivered courses on the probabilistic programming
        language Stan, data visualisation in Python, best-coding practices and how to
        implement them, and getting the most out of Posit (RStudio) Connect as a data
        scientist.}%

\end{itemize}

\clearpage




\cvsection{Skills}

\vspace{-.5em}
\begin{center}
    \begin{tabular}{@{}*{11}{c?}@{}}
        & Python & R & SQL & Stan & bash & git & Ansible & Terraform & Docker & Packer
    \end{tabular}
\end{center}

\begin{itemize}[
    itemsep=.2em,
    labelwidth=2em,
    leftmargin=2em,
    topsep=0em]

\item[\faIcon{bullhorn}]%
     {Confident and competent speaker; adept at communicating technical
     concepts and data insights to non-technical audiences.}%

\item[\faIcon{chart-line}]%
    {Strong numeracy skills, with an inherent understanding of Bayesian
     statistics, inference, model-fitting and prediction.}%

\item[\faIcon{git}]%
    {``Intermediate'' git user \& version control advocate, harnessing version
    control on all code-based projects, and using CI/CD tools to aid code
    stability, dictate release cycles, and enforce good-coding practices.}%

\item[\faIcon{database}]%
     {Hands-on experience writing and optimising SQL queries to form an ETL
     process.}%

\item[\faIcon{linux}]%
     {Capable of performing all manner of duties from a CLI, scripting in bash, and
      using standard command-line tools such as \texttt{ssh}, \texttt{grep},
      \texttt{sed}, \texttt{vi}, etc. for basic systems administration duties.}%


\end{itemize}



\cvsection{Community}

\begin{itemize}[
    itemsep=.2em,
    labelwidth=2em,
    leftmargin=2em,
    topsep=0em]

\item[\faIcon{users}]%
     {Chief-organiser and chair of
      \href{https://www.meetup.com/newcastle-upon-tyne-data-science-meetup/}%
           {North East Data Science meetup series},
      overseeing $\sim$50\% growth in group membership. Co-organiser of
      \href{https://www.meetup.com/north-east-databricks-meetup/}%
           {North East Databricks meetup series.}}

\item[\faIcon{stack-overflow}]%
     {Regular contributor on Stack Overflow---answering over 130 questions,
      reaching $>$340k users, and ranking in the top 8\% of overall users.}%

\item[\faIcon{mouse-pointer}]%
     {Maintainer of \href{https://\website}{\website}, a programming blog and
      personal website which attracts 800--1000 unique monthly users, with
      $\sim$85\% of traffic acquired through organic search.}

\end{itemize}

\cvsection{Awards}

\awarditem{British Data Awards}%
          {\href{https://predatech.co.uk/british-data-awards-2023-finalists-announced/}%{
                {Rising Star of the Year (finalist)}}%
          {March 2023}

\awarditem{Dynamites22}%
          {\href{https://www.dynamonortheast.co.uk/dynamites22-shortlist-unveiled/}%{
                {Rising Star (finalist)}}%
          {November 2022}

\awarditem{Northumbrian Water Hackathon}%
          {Best team solution}%
          {July 2019}

\awarditem{UK Conference on Multiscale Biology}%
          {Best poster award}%
          {April 2018}

\cvsection{References}

Available on request

\vfill
\hypersetup{urlcolor=light-grey}%
\color{light-grey}%
\rule{\textwidth}{1.25pt}

\footnotesize\raggedleft This CV was created with a custom \LaTeX{}
template. You can find its source at
\href{https://github.com/jwalton3141/CV}{github.com/jwalton3141/CV}.

\end{document}
